ESRC SDAI Application

### 2019-05-18 Draft.tex
update

Talk about CSEW

>>>>

The Crime Survey for England and Wales (CSEW) is an annual, representative survey collecting information on victims of crime across England and Wales, including 30,000--40,000 households every year (ref). The survey has a self-completion module containing questions about the respondent's experiences of domestic abuse throughout their life (since the age of 16), and in the past 12 months in particular (ref). Given the vast levels of underreporting characteristic to domestic abuse, the CSEW is the most reliable source of information on the prevalence of domestic abuse in England and Wales.

The two datasets have different merits allowing us to gain a deeper insight into the phenomenon and derive policy implications. The CSEW is more likely to give a better estimate of the true prevalence of domestic abuse, and contains rich demographic and socio-economic information on the respondent (victim).
